---
title: "p8105_hw6_zw2709"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = '90%'
)
theme_set(theme_minimal()+ theme(legend.position = 'bottom'))

options(
  ggplot2.continuous.colour = 'viridis',
  ggplot2.continuous.fill = 'viridis'
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2

Find some residuals

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  
  #convert numeric to factor
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"),
    babysex = as.factor(babysex),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"),
    frace = as.factor(frace),
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"),
    malform = as.factor(malform),
    mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other"),
    mrace = as.factor(mrace)
    
  )
    
```


There seems to have no missing data in the baby_df, and we could analyze the data using `r nrow(baby_df)` observations.




## fit a model

try to use linear regression model using all possible predictors and check the p value

```{r}
all_fit = lm(bwt ~ ., data = baby_df)
summary(all_fit)
```

And we might choose the model with predictors which is significant at 5% significance level, meaning the corresponding p value is less than 0.05

bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken


Therefore the fitted model and its information are as follows:

```{r}
mod_fit = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = baby_df)

broom::tidy(mod_fit) %>% 
  knitr::kable(digits = 3)
```



Then we need to make the plot based on the model residuals against the fitted values

Treat the residuals as y values and the predictions as x values

```{r}
baby_df %>% 
  add_predictions(mod_fit) %>% 
  add_residuals(mod_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3)+
  geom_smooth(method = "lm")
  
```



The residuals bounce around 0 and it seems to form a horizontal line around 0.



## Compare to two other models


* Model 1

bwt ~ blength + gaweeks
```{r}
one_fit = lm(bwt ~ blength + gaweeks, data = baby_df)

broom::tidy(one_fit) %>% 
  knitr::kable(digits = 3)
```



* Model 2

bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex

```{r}
two_fit = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = baby_df)

broom::tidy(two_fit) %>% 
  knitr::kable(digits = 3)
```



Cross validation

```{r}
cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble), 
    test = map(test, as_tibble)
  )
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    mod_fit = map(.x = train, ~lm(bwt~ babysex + bhead + blength + delwt + gaweeks + parity + smoken, data = .x)),
    one_fit = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    two_fit = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
    
  ) %>% 
  mutate(
    rmse_mod = map2_dbl(.x = mod_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_one = map2_dbl(.x = one_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_two = map2_dbl(.x = two_fit, .y = test, ~rmse(model = .x, data = .y))
  )
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```




The RMSE of model 1 is the largest, so it is not good fit because of large errors.
The model 2 and mod_fit has similar RMSE but mod_fit has smaller RMSE, so mod_fit would be the best model fit among the three ones.












